Forecasting future oil production in Norway and the UK: a general improved methodology

### 2014-06-24 Publications/Forecasting  Future Oil Production/peak_oil_3.tex
Merge branch 'master' of https://github.com/LucasFievet/Tomorrow
Conflicts:
	Publications/Forecasting  Future Oil Production/peak_oil.lyx~

As the total parameter space is too large to be sampled entirely,
a Monte Carlo technique is applied to compute the expected production
with confidence interval from future discoveries. In a nutshell, the
algorithm works as follows:
\begin{enumerate}
\item Draw a scenario (total number of fields in each size bin) based on its probability according to the likelihood function (\ref{eq:likelihood}). This is done by generating a random number $r$ between 0 and 1, and computing the scenario which is mapped to $r$ by the cumulative distribution function of all scenarios.
\item Compute the time distribution of new discoveries by fitting a logistic
curve for each size class.
\item For each discovery, generate a size and the resulting production curve
based on the size distribution and production curves of existing fields.
\item Superpose all the production curves.
\item Repeat and average over all drawn scenarios.
\end{enumerate}
The result is the expected production curve of future oil field discoveries.
The distribution of generated scenarios yields the confidence interval.

Last but not least, it has to be defined how the expected production from these future oil field discoveries is added to the extrapolated production from existing fields. The start of the simulation of new discoveries does not match up with the date of the latest production data. The reason being that the new fields (defined in section \ref{sub:Regular,-irregular-and}),
which are already discovered but did not yet enter the decay phase, are not taken into account in the simulation as their final size is not known. The only meaningful way of treating the new fields is to consider them as a discovery. Therefore, the starting point in time of the simulated production resulting from new discoveries has been choosen as the date in the past where it matches the current production from
new fields. In order words, the extrapolated production from regular and irregular fields added to the production from simulated future discoveries (which is shifted into the past as to match the production from new fields) must be equal to the current (latest available data) total production from all fields.

>>>>

As the total parameter space is too large to be sampled entirely,
a Monte Carlo technique is applied to compute the expected production
with confidence interval from future discoveries. In a nutshell, the
algorithm works as follows:
\begin{enumerate}
\item Draw a scenario based on its probability. {\bf DIDIER: Lucas, Peter expresses
that he does not understand how this is done. Please give more detail on 
how a scenario is chosen according to its probability and how the probability
is determined. A quick synthesis here would be useful.}
\item Compute the time distribution of new discoveries by fitting a logistic
curve for each size class.
\item For each discovery, generate a size and the resulting production curve
based on the size distribution and production curves of existing fields.
\item Superpose all the production curves.
\item Repeat and average over all drawn scenarios.
\end{enumerate}
The result is the expected production curve of future oil field discoveries.
The distribution of generated scenarios yields the confidence interval.

In order to account for the new fields discussed in section \ref{sub:Regular,-irregular-and},
which are already discovered but did not yet enter the decay phase,
the simulated production resulting from new discoveries has been shifted
to the date in the past where it matches the current production from
new fields. {\bf DIDIER: what is the meaning of ``shifted''? Peter does not fully
understand what is done here, neither do I..}
